---
title: "eds221-day4-comp1"
format: html
editor: visual
execute: 
  warning: false
---

## Functions

### Make a function that doubles a value.

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
  #can also code as 2 * my_dollars (do not need the print statement) but this is storing it as well
}
```

```{r}
double_value(10.13)
```

```{r}
double_value(my_dollars = 10.13, 5)

monthly_income <- c(13, 15, 16, 18)
```

### Create a function that returns an awesome restaurant name given a cool animal and your favorite food
```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees fahrenheit, write a function that converts it to Celsius


```{r}
convert_F_to_C <- function(fahrenheit) {
  x <- ((fahrenheit - 32) * (5/9))
  print(x)
}

convert_F_to_C(52)
```

### Create a function that given inputs of age and hometown, returns "I am __ years old and I'm from __"

```{r}
age_hometowm <- function(age_yr, hometown) {
  y <- paste("I am", age, "years old and I'm from", hometown)
  print(y)
}

age_hometowm(33, "Miami")
```

## print statement: show me this
## return statement: store and save so i can use later









